\speculake: Hiding Malware in Speculative Execution

### 2018-05-07 paper/payloads.tex
typos and wording fixes

\subsection{Virtual Machines}
We demonstrate in Section~\ref{subsec:turing} that general purpose computation 
is possible in the speculative environment in spite of the contraints 
imposed by the speculative world. However, a turing machine
is not an efficient or usable model for computation when
attempting to accomplish tasks on modern processors.

@@

To accommodate both developers as well as the unique constraints 
enforced by the speculative primitive, a custom emulation solution is required. 
we have approached this challenge by creating a custom instruction set -- 
SPASM -- which accommodates the speculative primitive specifically. This 
provides a higher level of abstraction around the speculative primitive
that we have used to implement various payloads.

>>>>

\subsection{Virtual Machines}
We demonstrate in Section~\ref{subsec:turing} that general purpose computation 
is possible in the speculative environment in spite of the constraints 
imposed by the speculative world. However, a Turing Machine
is not an efficient or usable model for computation when
attempting to accomplish tasks on modern processors.

@@

To accommodate both developers as well as the unique constraints 
enforced by the speculative primitive, a custom emulation solution is required. 
we have approached this challenge by creating a custom instruction set---
SPASM---which accommodates the speculative primitive specifically. This 
provides a higher level of abstraction around the speculative primitive
that we have used to implement various payloads.
